Supplementary Materials for \\ Modeling the competing effects of the immune system and EMT on epithelial cancers

### 2019-12-12 Paper/CleanPaper.tex
responded to adam's suggestions

TGF-$\beta$, an activator of EMT, is produced both by Tregs and tumor cells, thus connecting tumor-immune interactions with EMT, and as a result plays an important role in shaping tumor outcomes. EMT depends on TGF-$\beta$ concentration through a Hill-type function that determines the likelihood of EMT (or the reverse MET) through its magnitude relative to $\tau_{i-1}$. This is described by the equation:

@@

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure3/Figure3.pdf}}
\caption{Effects of mesenchymal tumor cell properties on the time to invasion. Trajectories of one patient per cohort including warmup and 2000 cell cycles for {\bf A.} mesenchymal immune evasion (MIE); {\bf A.} mesenchymal growth arrest (MGA); {\bf C.} Production of TGF-$\beta$ by Tregs.
{\bf D.} Survival curve corresponding to changes in the parameter MIE (A) for a patient cohort of 1000. Shaded region represents the 95\% confidence interval over the cohort. 
{\bf E.} Survival curve corresponding to changes in MGA.
{\bf F.} Survival curve corresponding to changes in Treg production of TGF-$\beta$. }
\label{fig:FirstSurvivalCurves}
\end{figure}

Mesenchymal tumor cells (MTCs) are characterized by changes in two parameters: mesenchymal immune evasion (MIE) and mesenchymal growth arrest (MGA). Here we assess the effects of each, alongside the effects of TGF-$\beta$ through its production by Tregs.  
%Both parameters are defined proportionally and hence lie in $[0,1]$, where higher values indicate more mesenchymal-like properties.
% $\Delta_\text{MIE}$ quantifies the reduction in probability that a mesenchymal cell will be subject to immune clearance.
% $\Delta_\text{MGA}$ quantifies the reduction in probability that a mesenchymal cell will proliferate, and is equivalent (in terms of its impact on the cell cycle) to an increased time spent in $G_0$.
%The cytokine TGF-$\beta$ is also involved in the EMT process (by increasing the probability of EMT). All three of these parameters were found to have large effects on the model by the Morris OAT analysis presented in Section \ref{SensAnalysis}. 
As MIE increases, the invasion-free survival decreases (Fig. \ref{fig:FirstSurvivalCurves}A) for all sets of parameters studied: as the subpopulation of invasive cells becomes more resistant to immune clearance, the tumor as a whole grows more resilient and thus can grow faster (Fig. \ref{fig:FirstSurvivalCurves}D).
\par
The relationship between MGA and invasion-free survival times displays a very different trend, and is non-monotonic with a local maximum appearing. For small values of MGA, increasing the MGA parameter results in increasing the invasion-free survival (Fig \ref{fig:FirstSurvivalCurves}B, E). However for large values of MGA, invasion-free survival times decrease. This is explored further below.
%This result is explored in Section \ref{KeyEMT}.
%As MGA increases, invasion-free survival increases: lower proliferation rates for mesenchymal cells slow down cancer progression (Fig \ref{fig:FirstSurvivalCurves}B).
%This is not intuitive, since decreased proliferation rates affects all mesenchymal cells, not just the invasive cells.
\par
TGF-$\beta$ varies according to its production by tumor cells and its production by Tregs. Here we assess the effects of varying the production of  TGF-$\beta$ by Tregs on invasion-free survival (Fig \ref{fig:FirstSurvivalCurves}B, E). We find, interestingly, that at lower production rates of TGF-$\beta$ lead to more rapid invasion or if it survives to a certain time point, a longer time to invasion.

>>>>

TGF-$\beta$, an activator of EMT, is produced both by Tregs and tumor cells, thus connecting tumor-immune interactions with EMT, and as a result plays an important role in shaping tumor outcomes.
To determine whether a cell undergoes EMT or MET, the TGF-$\beta$ is randomly divided among the cells so that associated with each cell $i$ is a value $\tau_i$.
This value is given by the following equation:

@@

For each cell, $\tau_i$ is summed with the current EMT score for that cell and if the result is above a threshold value, the cell undergoes EMT, otherwise MET.
This summation expresses the assumption that the epithelial and mesenchymal phenotypes are stable and cells will move along the EMT spectrum towards the equilibrium they identify as under typical conditions.
%This is then combined with the cell's EMT score and a threshold value determines if the cell subsequently undergoes EMT or MET.
%In doing this, we are assuming that the epithelial and mesenchymal phenotypes are stable and cells in a given type tend to move towards that 
%This represents cell-extrinsic sources shaping the trajectory of the cell along the EMT spectrum.
%Intrinsically, we assume that a cell is likely to keep its same phenotype, so we mesenchymal cells are more li
%If the difference is large enough, the cell undergoes EMT, otherwise it undergoes MET.
%This value $\tau_i$ is given by the following equation:
%EMT depends on TGF-$\beta$ concentration through a Hill-type function that determines the likelihood of EMT (or the reverse MET) through its magnitude relative to $\tau_{i}$. This is described by the equation:

@@

\begin{figure}
\center
{\includegraphics[width=0.85\textwidth]{Figure3/Figure3.pdf}}
\caption{Effects of mesenchymal tumor cell properties on the time to invasion. Trajectories of one patient per cohort including warmup and 2000 cell cycles for {\bf A.} mesenchymal immune evasion (MIE); {\bf B.} mesenchymal growth arrest (MGA); {\bf C.} Production of TGF-$\beta$ by Tregs.
{\bf D.} Survival curve corresponding to changes in the parameter MIE (A) for a patient cohort of 1000. Shaded region represents the 95\% confidence interval over the cohort. 
{\bf E.} Survival curve corresponding to changes in MGA.
{\bf F.} Survival curve corresponding to changes in Treg production of TGF-$\beta$. }
\label{fig:FirstSurvivalCurves}
\end{figure}

Mesenchymal tumor cells (MTCs) are characterized by changes in two parameters: mesenchymal immune evasion (MIE) and mesenchymal growth arrest (MGA). Here we assess the effects of each, alongside the effects of TGF-$\beta$ through its production by Tregs.  
%Both parameters are defined proportionally and hence lie in $[0,1]$, where higher values indicate more mesenchymal-like properties.
% $\Delta_\text{MIE}$ quantifies the reduction in probability that a mesenchymal cell will be subject to immune clearance.
% $\Delta_\text{MGA}$ quantifies the reduction in probability that a mesenchymal cell will proliferate, and is equivalent (in terms of its impact on the cell cycle) to an increased time spent in $G_0$.
%The cytokine TGF-$\beta$ is also involved in the EMT process (by increasing the probability of EMT). All three of these parameters were found to have large effects on the model by the Morris OAT analysis presented in Section \ref{SensAnalysis}. 
As MIE increases, the invasion-free survival decreases (Fig. \ref{fig:FirstSurvivalCurves}A) for all sets of parameters studied: as the subpopulation of invasive cells becomes more resistant to immune clearance, the tumor as a whole grows more resilient and thus can grow faster (Fig. \ref{fig:FirstSurvivalCurves}D).
\par
The relationship between MGA and invasion-free survival times displays a very different trend, and is non-monotonic with a local maximum appearing. For small values of MGA, increasing the MGA parameter results in increasing the invasion-free survival (Fig \ref{fig:FirstSurvivalCurves}B, E). However for large values of MGA, invasion-free survival times decrease. This is explored further below.
%This result is explored in Section \ref{KeyEMT}.
%As MGA increases, invasion-free survival increases: lower proliferation rates for mesenchymal cells slow down cancer progression (Fig \ref{fig:FirstSurvivalCurves}B).
%This is not intuitive, since decreased proliferation rates affects all mesenchymal cells, not just the invasive cells.
\par
\tcr{
TGF-$\beta$ varies according to its production by tumor cells and its production by Tregs. Here we assess the effects of varying the production of  TGF-$\beta$ by Tregs on invasion-free survival (Fig \ref{fig:FirstSurvivalCurves}C, F). We find that at lower production rates of TGF-$\beta$, the survival curve initially declines faster whereas higher production rates result in a steeper drop off in survival later. This is due to the possibility that the immune system rapidly clears the tumor upon influx of adaptive immune cells. A higher production of TGF-$\beta$ by the Tregs mitigates this possibility.
}

% lead to more rapid invasion or if it survives to a certain time point, a longer time to invasion.

### 2019-12-12 Paper/Supplement/CleanSupplement.tex
responded to adam's suggestions

\begin{document}
\maketitle
\tableofcontents

@@

\begin{table}[H]
\begin{center}
 \begin{tabular}{| c | c|} 
 \hline
 Name & Description  \\ [0.5ex] 
 \hline
 $p$ & proliferation rate of tissue cells \\ 
 \hline
 $d_C$  & death rate of tissue cells \\
 \hline
$\Delta_\text{MIE}$ &  mesenchymal immune evasion \\
 \hline
 $\Delta_\text{MGA}$ & mesenchymal growth arrest    \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation\\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell\\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has \\
  \hline
  $K_4$ & EC50 term for TGF-$\beta$ activation of Tregs \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants \\
  \hline
  $\sigma_\text{NK}$ & NK source rate \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell \\ 
  \hline
  $d_\text{NK}$ & NK death rate  \\ 
  \hline
  $d_\text{CTL}$ & CTL death rate \\ 
  \hline
  $d_\text{Treg}$ & Treg death rate \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate  \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives  \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive \\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells\\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg\\
  \hline
\end{tabular}
  \caption{The model parameter names and descriptions. Note that many of these values are affected by the inflammation state of the system.}
\end{center}
\end{table}

@@

\begin{longtable}{| c | p{5cm} | m{3cm} | m{3cm} |} 
 \hline
 Name & Description & INFL Low Value & INFL High Value  \\ [0.5ex] 
 \hline\hline
  $p$ & weight of proliferation for tissue cells & 0.28 & \\ 
 \hline
 $d_C$  & weight of apoptosis for tissue cells & 0.14 & \\
 \hline
$\Delta_\text{MIE}$ & MIE & 0.6 & \\
 \hline
 $\Delta_\text{MGA}$ & MGA  & 0.2 &  \\
 \hline
  $\Delta_A$ & proportional decrease to weight of apoptosis for cells with mutated apoptosis pathway & 0.3 &  \\
  \hline
  $\Delta_\text{IE}$ & proportional increase to weight of immune evasion for cells with mutated immune evasion pathway & 0.48 &  \\
  \hline
  $\Delta_P$ & proportional increase to weight of proliferation for cells with mutated proliferation pathway & 0.36 &  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation & 80 cells& \\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell & 8 cells& \\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions & 5 cells / volume & 0.025 cells / volume \\
  \hline
  $K_3$ & EC50 term for cumulative absorption of TGF-$\beta$ & 200 amount / volume & \\
  \hline
  $K_4$ & EC50 term for TGF-$\beta$ activation of Tregs & 50 amount / volume & \\
  \hline
 $E_\text{NK}$ & weight of NKs clearing mutants & 10 & 30  \\
  \hline
  $E_\text{CTL}$ & weight of CTLs clearing mutants & 200 & 600 \\
  \hline
  $\sigma_\text{NK}$ & NK source rate & 1.3 cells / cycle &  \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell & 100 cells / (cleared mutants $\times$ cycles)& \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell & 200 cells / (cleared mutants $\times$ concentration of TGF-$\beta$ $\times$ cycles)& \\ 
  \hline
  $d_\text{NK}$ & NK death rate & 0.13 / cycle &  \\ 
  \hline
  $d_\text{CTL}$ & CTL death rate & 0.0260 / cycle& \\ 
  \hline
  $d_\text{Treg}$ & Treg death rate & 0.0260 / cycle& \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate & 0.01 / concentration of TGF-$\beta$ & \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives & 6 concentration of TGF-$\beta$ & \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive & 500 concentration of TGF-$\beta$ &\\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells & 0.05 concentration of TGF-$\beta$ / cell / cycle& \\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg & 0.5 concentration of TGF-$\beta$ / cell / cycle& \\
  \hline
  & RP Cancer Line  & 0.5 &  \\ 
 \hline
&  INFL High Duration & 30 cycles&   \\
 \hline
 & INFL Low Duration &30 cycles&   \\
 \hline
& Mes Threshold & 0.7 &    \\
 \hline
  & maximum initial mutation damage after warmup  & 0.01 &\\
  \hline
  & increase in probability to mutate for non-mutating proliferating cells & 0.0001 & \\
  \hline
  \caption{The model parameter names, descriptions, and values during both low and high inflammation. Parameters with only one value do not change with the inflammatory state.}
\end{longtable}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/SKCM.pdf}}
\caption{A. K-means clustering of SKCM using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of SKCM using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of SKCM using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:SKCM}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/LIHC.pdf}}
\caption{A. K-means clustering of LIHC using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of LIHC using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of LIHC using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:LIHC}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/LUAD.pdf}}
\caption{A. K-means clustering of LUAD using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of LUAD using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of LUAD using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:LUAD}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure1/SinglePatientBlue.jpg}}
\caption{
Single patient trajectory without immune cells targeting premalignant cells. Compare to Fig. 1B.
}
\label{fig:1b_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure1/OneSurvivalCurve.jpg}}
\caption{
Sample cohort survival curve without immune cells targeting premalignant cells. Compare to Fig. 1C.
}
\label{fig:1c_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure2/Figure2.jpg}}
\caption{
Morris-OAT global sensitivity without immune cells targeting premalignant cells. Compare to Fig. 2.
}
\label{fig:2_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure3/Figure3_first.pdf}}
\caption{
Effects of mesenchymal tumor cell properties on the Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 3.
}
\label{fig:3_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure4/Figure4_first.pdf}}
\caption{
Effects of inflammation on the Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 4.
}
\label{fig:4_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure5/MIEvsMGA_bigcbar.jpg}}
\caption{
Summary of the contrasting effects of MIE and MGA on Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 5.
}
\label{fig:5_first}
\end{figure}

>>>>

\begin{document}
\maketitle
\tableofcontents
\listoftables
\listoffigures

@@

\begin{table}[H]
\begin{center}
 \begin{tabular}{| c | c|} 
 \hline
 Name & Description  \\ [0.5ex] 
 \hline
 $p$ & proliferation rate of tissue cells \\ 
 \hline
 $d_C$  & death rate of tissue cells \\
 \hline
$\Delta_\text{MIE}$ &  mesenchymal immune evasion \\
 \hline
 $\Delta_\text{MGA}$ & mesenchymal growth arrest    \\
 \hline
  $\Delta_A$ & mutant cells decreased apoptosis  \\
  \hline
  $\Delta_\text{IE}$ & mutant cells increased immune evasion  \\
  \hline
  $\Delta_P$ & mutant cells increased proliferation  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation\\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell\\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions  \\
  \hline
  $K_3$ & EC50 term for how much TGF-$\beta$ each cell has \\
  \hline
  $K_4$ & EC50 term for TGF-$\beta$ activation of Tregs \\
  \hline
 $E_\text{NK}$ & rate of NKs clearing mutants  \\
  \hline
  $E_\text{CTL}$ & rate of CTLs clearing mutants \\
  \hline
  $\sigma_\text{NK}$ & NK source rate \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell \\ 
  \hline
  $d_\text{NK}$ & NK death rate  \\ 
  \hline
  $d_\text{CTL}$ & CTL death rate \\ 
  \hline
  $d_\text{Treg}$ & Treg death rate \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate  \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives  \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive \\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells\\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg\\
  \hline
\end{tabular}
  \caption[Parameter names and descriptions]]{The model parameter names and descriptions. Note that many of these values are affected by the inflammation state of the system.}
\end{center}
\end{table}

@@

\begin{longtable}{| c | p{5cm} | m{3cm} | m{3cm} |} 
 \hline
 Name & Description & INFL Low Value & INFL High Value  \\ [0.5ex] 
 \hline\hline
  $p$ & weight of proliferation for tissue cells & 0.28 & \\ 
 \hline
 $d_C$  & weight of apoptosis for tissue cells & 0.14 & \\
 \hline
$\Delta_\text{MIE}$ & MIE & 0.6 & \\
 \hline
 $\Delta_\text{MGA}$ & MGA  & 0.2 &  \\
 \hline
  $\Delta_A$ & proportional decrease to weight of apoptosis for cells with mutated apoptosis pathway & 0.3 &  \\
  \hline
  $\Delta_\text{IE}$ & proportional increase to weight of immune evasion for cells with mutated immune evasion pathway & 0.48 &  \\
  \hline
  $\Delta_P$ & proportional increase to weight of proliferation for cells with mutated proliferation pathway & 0.36 &  \\
  \hline
 $K_0$ & EC50 term for negative feedback of tissue cells on own proliferation & 80 cells& \\
 \hline
 $K_1$ & EC50 term for probability of NK cell finding mutant cell & 8 cells& \\
 \hline
  $K_2$ & EC50 term for Treg inhibition of cytotoxic functions & 5 cells / volume & 0.025 cells / volume \\
  \hline
  $K_3$ & EC50 term for cumulative absorption of TGF-$\beta$ & 200 amount / volume & \\
  \hline
  $K_4$ & EC50 term for TGF-$\beta$ activation of Tregs & 50 amount / volume & \\
  \hline
 $E_\text{NK}$ & weight of NKs clearing mutants & 10 & 30  \\
  \hline
  $E_\text{CTL}$ & weight of CTLs clearing mutants & 200 & 600 \\
  \hline
  $\sigma_\text{NK}$ & NK source rate & 1.3 cells / cycle &  \\ 
  \hline
  $\sigma_\text{CTL}$ & CTL source rate per cleared mutant cell & 100 cells / (cleared mutants $\times$ cycles)& \\ 
  \hline
  $\sigma_\text{Treg}$ & Treg source rate per cleared mutant cell & 200 cells / (cleared mutants $\times$ concentration of TGF-$\beta$ $\times$ cycles)& \\ 
  \hline
  $d_\text{NK}$ & NK death rate & 0.13 / cycle &  \\ 
  \hline
  $d_\text{CTL}$ & CTL death rate & 0.0260 / cycle& \\ 
  \hline
  $d_\text{Treg}$ & Treg death rate & 0.0260 / cycle& \\ 
  \hline
  $k_\text{EMT}$ & EMT/MET rate & 0.01 / concentration of TGF-$\beta$ & \\
  \hline
  $\sigma$ & standard deviation of noise in TGF-$\beta$ each cell receives & 6 concentration of TGF-$\beta$ & \\
  \hline
 $\tau_\text{max}$ & max amount of TGF-$\beta$ any cell can receive & 500 concentration of TGF-$\beta$ &\\
  \hline 
 $\tau_\text{MUT}$ & rate of TGF-$\beta$ production by mutant cells & 0.05 concentration of TGF-$\beta$ / cell / cycle& \\
  \hline
 $\tau_\text{Treg}$ & rate of TGF-$\beta$ production by Treg & 0.5 concentration of TGF-$\beta$ / cell / cycle& \\
  \hline
  & RP Cancer Line  & 0.5 &  \\ 
 \hline
&  INFL High Duration & 30 cycles&   \\
 \hline
 & INFL Low Duration &30 cycles&   \\
 \hline
& Mes Threshold & 0.7 &    \\
 \hline
  & maximum initial mutation damage after warmup  & 0.01 &\\
  \hline
  & increase in probability to mutate for non-mutating proliferating cells & 0.0001 & \\
  \hline
  \caption[Parameter values]{The model parameter names, descriptions, and values during both low and high inflammation. Parameters with only one value do not change with the inflammatory state.}
\end{longtable}

%%%%%%%%%%%%%%%%
% Figures
%%%%%%%%%%%%%%%%

\begin{figure}
\center
{\includegraphics[width=1\textwidth]{../Figs/Figure1/SI_fig1.pdf}}
\caption[Fig. 1BC without targeting premalignant cells]{
A. Single patient trajectory without immune cells targeting premalignant cells. Compare to Fig. 1B. B. Sample cohort survival curve without immune cells targeting premalignant cells. Compare to Fig. 1C.
}
\label{fig:1_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure2/Figure2.jpg}}
\caption[Fig. 2 without targeting premalignant cells]{
Morris-OAT global sensitivity without immune cells targeting premalignant cells. Compare to Fig. 2.
}
\label{fig:2_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure3/Outdated/Figure3_first.pdf}}
\caption[Fig. 3 without targeting premalignant cells]{
Effects of mesenchymal tumor cell properties on the Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 3.
}
\label{fig:3_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure4/Figure4_first.pdf}}
\caption[Fig. 4 without targeting premalignant cells]{
Effects of inflammation on the Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 4.
}
\label{fig:4_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure5/MIEvsMGA_bigcbar.jpg}}
\caption[Fig. 5 without targeting premalignant cells]{
Summary of the contrasting effects of MIE and MGA on Time to Cancer without immune cells targeting premalignant cells. Compare to Fig. 5.
}
\label{fig:5_first}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/SKCM.pdf}}
\caption[SKCM TCGA Data Analysis]{A. K-means clustering of SKCM using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of SKCM using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of SKCM using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:SKCM}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/LIHC.pdf}}
\caption[LIHC TCGA Data Analysis]]{A. K-means clustering of LIHC using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of LIHC using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of LIHC using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:LIHC}
\end{figure}

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/LUAD.pdf}}
\caption[LUAD TCGA Data Analysis]{A. K-means clustering of LUAD using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of LUAD using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of LUAD using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:LUAD}
\end{figure}
